---
title : "EFDC Variables"
author: "Dynamic Solutions International, LLC"
output: bookdown::gitbook
date: "2017-03-29"
description: This document lists the variables used in EFDC model. 
---
  
# Preface

This document is prepared by Dynamic Solutions International, LLC to support the "EFDC Theory knowledge base" hosted on [Confluence](https://dynamicsolutions-intl.atlassian.net/wiki/spaces/ETG). This document is compiled based on the years experience with EFDC model. This document is released in the hope that the EFDC community will find this document as a valuable resource in understanding EFDC model and its variable better. 

```{r, echo=FALSE, eval=FALSE}
bookdown::render_book("index.Rmd","bookdown::gitbook", output_dir = "docs")
```

# Arrays

## Combined Arrays
```{r, echo=FALSE, warning=FALSE}
array <- read_excel("data/2017-03-29-arrays-rearranged.xlsx", sheet = "arrays", col_types = NULL)
DT::datatable(array, rownames = F)
```

## 1-D Arays
The arrays above are separated into 1-D arrays in this section. 
The following tables displays 1-D arrays in EFDC code. 

```{r, echo = FALSE, warning=FALSE}
oned <- read_excel("data/2017-03-29-arrays-rearranged.xlsx", sheet = "1darray")
DT::datatable(oned, rownames = F)
```

## 2-D Arrays

```{r, echo = FALSE, warning = FALSE}
twod <- read_excel("data/2017-03-29-arrays-rearranged.xlsx", sheet = "2darray")
DT::datatable(twod, rownames = F)
```

## 3-D Arrays
```{r, echo = FALSE, warning = FALSE}
threed <- read_excel("data/2017-03-29-arrays-rearranged.xlsx", sheet = "3darray")
DT::datatable(threed, rownames = F)
```

## 4-D Arrays

```{r, echo = FALSE, warning = FALSE}
fourd <- read_excel("data/2017-03-29-arrays-rearranged.xlsx", sheet = "4darray")
DT::datatable(fourd[,-2], style = 'bootstrap', width = 1200, rownames = F)
#knitr::kable(fourd, format="html", pad=0)
```